---
output:
  pdf_document:
    latex_engine : pdflatex
params:
  orcid: ""
  role: ""
  hospital: ""
  team: ""
header-includes:
- \usepackage[fontsize=11pt]{scrextend}
- \pagenumbering{gobble} # stop autopage numbering
  
---
```{r setup, include=FALSE, fig.align="center"}
knitr::opts_chunk$set(echo = TRUE)

source('~/collaborator/R/orcid_pull_name.R')

```

```{r recon_logo, echo=FALSE, message=FALSE, fig.align="center"}
library(dplyr); library(magick)
# imager::load.image("https://raw.githubusercontent.com/kamclean/starsurg/master/recon_logo.png") %>%
#  as.raster() %>%
#  plot()

magick::image_read("https://raw.githubusercontent.com/kamclean/starsurg/master/recon_logo.png") %>%
  magick::image_scale("600")
```

\centering

## This is to certify that

# **`r orcid_pull_name(params$orcid, initials=FALSE)$full_name_orcid`**

(ORCID: `r params$orcid`)

## was a **`r params$role`** in the **RECON audit** at

# **`r params$hospital`**

## within the **`r params$team`** team

\raggedright

Displaying skills in: 
  
- Identifying and recruiting patients to a national database.

- Determining accurate pre-operative, operative and follow up data from clinical notes.

- Collaboration with other members of their "mini-team" to collect data.

\centering

&nbsp;

With warm thanks from the

**Student Audit and Research in Surgery (STARSurg) Steering Committee**

Generated on **`r format(Sys.time(), '%d %B %Y')`**

***
```{r recon_sponsors, echo=FALSE, message=FALSE, fig.align="center"}
library(dplyr); library(magick)
magick::image_read("https://raw.githubusercontent.com/kamclean/starsurg/master/recon_sponsors.png") %>%
  magick::image_scale("800")
```
